---
title: "Planning Studies with the studyplanner Package"
author: "Your Name"
date: "`r format(Sys.Date())`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Planning Studies with the studyplanner Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Overview

studyplanner implements utilities we used previously: adjusted effect size for baseline-follow-up designs, two-arm power/sample size, sensitivity grids, and budget optimization.

Adjusted effect size

For baseline–follow-up correlation rho, single-timepoint SD sigma, and expected difference in annual change Delta,

```{r}
library(studyplanner)
d <- effect_size_adj(delta = 0.05, sigma = 0.2, rho = 0.9)
d
```
Power at a given sample size
```{r}
power_two_arm(d_adj = d, n = 100, alpha = 0.05)
```

Solve for sample size
```{r}
sample_size_two_arm(d_adj = d, alpha = 0.05, target_power = 0.8)
```
Cost and budget optimization
```{r}
study_cost(n = 120, cost_per_subject = 10000, fixed_costs = 5000)
opt <- optimize_under_budget(d, alpha = 0.05, budget = 1000000, cost_per_subject = 10000, fixed_costs = 5000)
opt
```
Sensitivity grid
```{r}
plan_grid(delta_vec = c(0.04, 0.05), sigma_vec = c(0.18, 0.2), rho_vec = c(0.85, 0.9), n_vec = c(80, 120),
alpha = 0.05, cost_per_subject = 10000, fixed_costs = 5000)
```
